% ******************************* Thesis Dedication ********************************

\begin{acknowledgements}
I owe so much to so many people. This thesis took \textit{much} longer than I had ever hoped it would take to write, so I come to my acknowledgements page weighed down with gratitude.

First and foremost, I am immensely grateful to Dr Jane Midgley and Dr Alexander Wilson, who picked me up like a stray cat in the final five months of my thesis when I was facing yet another supervisory change. The past five months under your supervision have been nourishing and encouraging and you have been wonderful companions in the journey of finishing this thesis. Thanks are due also to the rest of the rotating cast of supervisors I have had throughout the past five years—to Dr Clara Crivellaro, Prof. Roger Burrows, Prof. Pete Wright, Dr Jan Smeddinck, Dr Rachel Clarke, and Prof. Jeremy Crampton. This thesis bears the mark of your hands on it in some form or another. Thanks are particularly due here to Roger and Rachel, who helped shape my ethnography, design, and writing the most before these final few months.

I would love to thank all the members of Cohort 4 of Open Lab's Digital Civics CDT. A special thanks is due to Rebecca Nicholson, James Hodge, Hazel Dixon, Megan Venn-Wycherley, and Erkki Hedenborg, who have been there through absolutely everything. From the harrowing days of our Master's (\textit{"where's the digital?"}) right up to today, you have been an incomparable group of people to learn, work, and struggle alongside. I wouldn't have wanted to do it with anyone else.

To the other members of Open Lab who have provided support, mentorship, or friendship over the years—Sean Peacock, Jazz McCoull, Daniel Parry, Angelika Strohmayer, Matt Marshall, Rosie Bellini, Mohaan Biswas, Sunil Rodger, and Alex Bowyer chief among them—thank you for being bright beams of light in the dark.

To academics from all over who acted as mentors and/or friends, such as Mariam Asad, Oliver Bates, Os Keyes, Miranda Iossifidis, Velvet Spors, Corinne Cath-Speth, Paris Selinas, and Cally Gatehouse; thank you for acting as a sounding board, a fellow traveller, or pointing me in the right direction.

All of my participants have my eternal appreciation for letting me hear and steward your stories and experiences. Rachel, Holly, David, Fran, Sohila, and Claire acted as brilliant guides for me in unfamiliar territory. Thanks also are due to many others who I can't name as clearly in order to preserve their privacy. If I have worked with you over the past six years, I want you to know that you have profoundly impacted not only my research but the way that I live my life. I am similarly grateful to my many young participants, but particularly B, C, A, and L. Your stories will always stay with me.

The friends who have seen me through this thesis are patient beyond compare. To the denizens of Osborne Avenue, Mark, Oytun, Leonie, Laura, and Troy—thank you for welcoming me to a new city and starting me off on the right foot. To Rachel and Nat—thank you for bearing with me when our living room was an office and we couldn't leave the house. To my D\&D group—Szofia, Kat, Charlie, Paul, and Jess—thank you for providing just the right level of distraction. To the Cornwall contingent—Sarah, Harri, and Ciaran—thank you for being there for me when I needed you and picking me up from some pretty terrible places. To Kitson, Eve, Daisie, and Harith, who frustratingly don't group nicely into any other category—I am so grateful to know people like you who look at the world in the same way as me and who have always been ready to talk about whatever new fascination I have. To Iain and Kate—thank you for the countless coffees that have fuelled the writing of this thesis. Iain—I don't know where \textit{fractured signals} would have got to without our chats at the shop door during the pandemic. To my co-workers at fractals co-op, Oliver, Leah,  and Hazel—thank you for supporting me to finish this whilst we build our practice together, and thank you for being the best co-workers a person could ask for.

To Dean Pomeroy—I do this work so we can build a new world together that doesn't feel like the old one. So many of the ideas in this thesis started with you: on a three hour phone call, on a drive to Praa Sands at midnight, or traipsing halfway across New York to go to an open mic. Thank you for every late night ramble about theory, every harebrained art project, and for being my personal hype man.

I have been so incredibly lucky to have a partner like Chloe Eastabrook, who has been by my side for every moment of this journey, from Osborne Avenue to now, and who has been my biggest cheerleader throughout. Her unwavering support, belief, and encouragement in me has been a source of strength through some of the hardest moments. Thank you for always being curious, and loving, and patient, and for listening to endless hours of theoretical discussions about things I'm \textit{sure} you don't care about. Your attention is infinitely valuable. 

This thesis is dedicated to Dr Joanie Willett and Dr Karen Scott, who first sparked my curiosity about how theory could build a different kind of world. 

This research was funded by the EPSRC Centre for Doctoral Training in Digital Civics (EP/L016176/1).
\end{acknowledgements} 
