\begin{covid}
The COVID-19 pandemic and the lockdown measures taken to protect public health had a significant impact on the latter stages of the research presented in this thesis. I was in my second year of research when the first lockdown began in March 2020. Due to the lockdown, inability to travel, and social distancing measures, neither my ethnographic nor design-led methods were initially viable in this context. I had been planning to undertake research in the summer that would refine the methods I present in chapter \ref{ch:7}, which would lead to a final design project which would be the culmination of my work. I re-planned my data collection three times: first, to take into account possibly having to deliver workshops remotely using Zoom and the digital canvas tool Miro (this did not happen); second, I collected data about the impact of COVID-19 on social care workers to ensure that I had more data on these experiences if I needed them (this does not feature in the thesis); and finally, to take the form of the design project that is presented in chapter \ref{ch:8}. This final change was due to the availability and capacity of the organisations I had been working with up until that point, as they had to step back from research due to the severity of the pandemic for their service users. I lost considerable time to each of these adaptations to my data collection plans. 

I needed to make changes to my research questions and my thesis' emergent argument thesis due to these changes. Originally, one of my research questions focused on the role that digital technologies and the people designing and developing them play in the context of the third sector. This was an element that I had planned to explore through follow-up ethnography with service design teams within the organisations I had been working with. As this was no longer viable due to the pandemic, I had to remove this aspect from my thesis and focus entirely on the development of a novel methodology.

Despite the changes brought to my research by the COVID-19 pandemic, I am confident in the final thesis that I am presenting here, and the pandemic context proved particularly salient for the development of an assemblage of methods focused on envisioning alternate futures and imagining multiple timelines. 
\end{covid}