\chapter{Conclusion}
\label{ch:9}

\section{Introduction}
\label{sec:}
In the previous chapter, I detailed the \textit{fractured signals} project. Building on the insights developed in the \emph{It's Our Future} project, the \emph{fractured signals} project supported workers who work with care-experienced young people to identify issues with their contemporary world, work towards the development of critical consciousness, imagine different futures, and begin to identify ways to work towards these futures. I refer to this approach as speculative praxis, and suggest that this can be used as a method assemblage to support people to mitigate, resist and construct alternatives to austerity-intensified capitalist realism through targeted creative deterritorialization. 

In this chapter, I identify how speculative praxis constitutes a response to the problems posed by austerity-intensified capitalist realism and the justification, classification, and discursive accumulation practices it engenders. I begin this chapter by identifying how this thesis has answered the research questions presented at the outset, and review the thesis' central contributions. I dig deeper into the implications of these contributions and the concepts I have presented, including the applicability of these ideas outside of the space of the third sector/care provision, and suggest some directions for further work in the space. Finally, I present some limitations of this work and of capitalist realism's usefulness as an analytic in our contemporary context.

\section{Research questions and contributions to knowledge}
In chapter \ref{ch:1}, I presented this thesis' research questions. These were:
\begin{itemize}
    \item What experiences and affects does capitalist realism elicit?
    \item How does capitalist realism operate to make these experiences and affects possible (or probable)?
    \item How can the tools and methods of design be used to respond to the challenges presented by capitalist realism?
\end{itemize}
In this section, I will detail the answers that I have provided through this thesis to each of these questions in turn, and the contributions to knowledge that I have made, before reviewing the contributions of the thesis as a whole.

\subsection{What experiences and affects does capitalist realism elicit?}
\label{subsec:9-2-1}
Although each chapter provides some insight on each of these questions, the first research question was primarily addressed in chapters \ref{ch:2} and \ref{ch:5}. In chapter \ref{ch:2}, I began by describing capitalist realism. I provided a richer theoretical basis for what capitalist realism is, how it operates, and its relevance to the sociopolitics of the 2010s through \citet[p. 6]{shonkwiler_reading_2014}’s understanding of the components of capitalist realism. These are capital’s ability to:
\begin{quote}
\begin{itemize}
\item  constantly revolutionize its sources of and strategies for accumulation, developing new configurations of activity;
\item have an economic, social and affective life that has vast consequences for our lived experiences;
\item and to transform this constant change and lived experience into a widely accepted brand of Gramscian `common sense'.
\end{itemize}
\end{quote}
I explored each of these components of capitalist realism in turn, and argued that austerity is both exemplary of capitalist realism and an intensifier of it. First, I turned towards the economic, social, and affective life of capitalist realism, by detailing the instability created by changing economics. I surveyed the changes brought about to work and labour by Fordism and the advent of the disciplinary society (characterised by enclosure, repetition, and routine), before following the advent of neoliberalism and its transformation of work into post-Fordism and the control society (characterised by flexibility, spontaneity, and instability). I argued that these made possible new sources of and strategies for capital accumulation. Drawing on \citet{marx_capital_2004}, \citet{luxemburg_accumulation_2015}, and \citet{harvey_new_2003}, I described how capital requires the presence or creation of an `outside' into which it can expand in order to maintain hegemony \citep{gramsci_selections_2007}. I described how \citet{fisher_capitalist_2009} presents this in capitalist realism as capital's ability to "precorporate" resistance to it, creating trends of resistance to capital that are easily incorporable into it. Finally, I presented the way that this transforms into a Gramscian "common sense" through the creation of an affect of reflexive impotence \citep[p. 24]{fisher_capitalist_2009}, in which people recognise that "things are bad" but feel as if they cannot do anything about it. This felt sense of powerlessness leads to a "slow cancellation of the future" \citep[p. 5]{fisher_ghosts_2014}, in which it feels impossible to imagine a future that is any different from our present reality.

I continued to explore capitalist realism with reference to the third sector under the fiscal austerity that emerged in the UK in response to the 2008 financial crisis. Austerity led to huge funding cuts for both public and third sector organisations, and introduced a deepened conditionality to funding  which made organisations compete with each other to best demonstrate how they provide "value for money" \citep{clifford_charitable_2017, jones_uneven_2016, clayton_distancing_2016}. This engendered a shift in people's experiences, as affective atmospheres of frustration, disappointment and anxiety circulated \citep{hitchen_living_2016} and shaped people's capacities for action. These constituted austerity's economic, social, and affective shifts, and the way that these shifts create a "common sense" around the impossibility of change. I proposed that austerity's accumulative action was therefore in the production of vulnerability itself—that the new sources of accumulation were people who required support services  (which increased as a result of austerity), and the strategy for capital accumulation was through third sector organisations classifying people as vulnerable, limiting their capabilities to the point that their accumulative activity could continue. 

In chapter \ref{ch:5}, I explored the paradigm of third sector organisations under austerity-intensified capitalist realism in practice, through the case of \textit{The Charity} and their three projects Small Steps, Building Bridges, and Seabird, in order to explore the experiences and affects elicited by capitalist realism in a practical context. I conducted an ethnographic study of frontline support workers, and young people perceived to be vulnerable within these projects. I highlighted how the value for money agenda forces support organisations to change their perceived efficacy in relation to work, labour, time, or money. In The Charity, these formed three consistent experiences for workers—there not being enough labour to do the amount of work there is, there not being enough time to do the amount of work there is, or there not being enough money to source a sufficient amount of labour. In this chapter, I focused on only the first of these in the interests of length—what workers' experiences of there being `too much work' was. I identified how this led to workers doing work that they aren't trained for, experiencing a need for a high amount of emotional labour, and being subject to the control techniques of their managers to ensure they get the work done. I then turned to understanding the experiences of young people perceived to be vulnerable within this, and identified how their agency was disregarded through inadequate forms of listening, and how this leads to young people not receiving the right support, leading to them feeling isolated, confused, and anxious. I identified a level of consistency between the affects experienced by workers, young people, and managers: they felt anxious, confused, distrustful and powerless. Managers and workers struggle to build trusting relationships with each other, whilst workers and young people struggle in a similar way. Managers use control techniques on their workers to ensure work gets done, whilst workers use similar techniques on young people to offer limited support or make them `engage'. Young people feel isolated, disoriented, "broken down" and powerless, whilst workers feel individualised, anxious, in "panic mode", and unable to leave their jobs. The answer to my first research question is that austerity-intensified capitalist realism elicits experiences that are grounded in the scarcity created by the value for money agenda, and results in the creation of affects centered on separation, confusion, and instability.

The contribution that I have made through answering this research question is a deeper exploration of capitalist realism's theoretical and material basis, providing a richer picture of its impacts that is grounded in ethnographic observation rather than cultural theory. Capitalist realism is a useful lens through which to understand the sociopolitics of the late 2000s and the 2010s, and its initial grounding in cultural theory and anecdotal observation in the work of \citet{fisher_capitalist_2009} has led to a dearth of its use within more ethnographic academic traditions such as geography or sociology. By more deeply theorising about \textit{how} capitalist realism came to dominance and collecting primary data about the experiences of people living under capitalist realism, there is an opportunity for it to become a more prominent analytic through which to view this period of time. Although a good amount of work already exists drawing upon capitalist realism as an analytic of media and cultural outputs, such as advertising \citep{schudson_advertising_2013}, movies, \citep{flisfeder_love_2017}, literature \citep{tally_jr_for_2022}, and television \citep{la_berge_capitalist_2010}, there is comparatively little published on capitalist realism as it pertains to social policy, service provision, or austerity. The insights that I have provided in this thesis on  capitalist realism's intellectual ancestry and the experiences it engenders suggest a wider applicability of capitalist realism as an analytic. It also helps to provide a unifying frame for much research that may otherwise appear distinct—for example, research about the experiences of workers responding to an economic change (in the form of capitalist realism) has a direct relationship to research about young people receiving poor support services or finding it difficult to imagine a future for themselves.  

\subsection{How does capitalist realism operate to make these experiences and affects possible (or probable)?}
\label{subsec:9-2-2}
I answered my second research question in chapter \ref{ch:6}, where I detailed the mechanics of the systems that sustain austerity-intensified capitalist realism. To answer the question of how capitalist realism makes these experiences and affects possible (or probable), I continued my ethnographic research with The Charity. I identified the call for a "common measurement framework" for organisations engaged in youth service provision \citep[p. 4]{house_of_commons_education_committee_services_2011} as a significant inflection point, as it both set a standard for youth service provision going forward and amplified a set of measurement and evaluation practices that were already circulating at the time. This renewed focus on evaluation led to service provision being more deeply understood in terms of "outcomes" and "outputs" and a greater use of tools and technologies such as the Outcomes Star and theories of change to make sense of programmes. In this chapter, I presented the grounded theory of justification, classification, and discursive accumulation practices as a descriptor of the changes brought about by this renewed focus on evaluation, and as the central mechanism through which austerity-intensified capitalist realism makes the aforementioned experiences and affects probable. Justification practices describe how the work of evaluation (whether through skilled or unskilled workers) becomes focused on the act of justifying the efficacy of the programme, not on the act of authentically evaluating it. Skilled evaluators tell an edited, clarified story of the programme, presenting the work done in its best possible light. Unskilled evaluators rely on data that may have been collected with little consideration of context, questioning, or bias. Both present a justification of the programme's work rather than an effective evaluation of it.

Justification practices occur alongside classification practices, and both represent an attempt to make youth service provision appear closer to a scientific practice. Justification practices describe what changes can be made in a given project and why, whilst classification practices seek to establish who this intervention could be successful for, and what different types of intervention might have in common. Classification practices are the central mechanism through which the figure of the vulnerable subject is produced. Under austerity-intensified capitalist realism, a dual classification system occurs, distinguishing between the types of vulnerable people that exist and the types of intervention that might work to support these different types of vulnerability. Classifications may exist based on age, type of need, or lived experiences, and types of intervention are imagined to be entirely separate even though someone may have overlapping needs or experiences. Classification based on identity (or kinds of lived experiences) is common within the sector, and can lead to young people internalising these classifications, the stigma attached to them, and limiting their own capabilities in turn. 

The professionalisation of youth service provision that has happened as a result of the move towards "value for money" and evaluation has resulted in an increased performativity within the third sector and led to accumulative activity that is discursive in nature. This discursive accumulation can be near-endless, as the surplus value that can be extracted from accumulation is performative, and does not need to directly relate to a material thing. One form of this discursive accumulation is the focus on the construction of `best practice' through co-production and innovation, despite projects often failing to live up to their ideals of co-production. Despite the performance of being co-productive, The Charity often sidelined co-production in favour of reaching their other organisational objectives. This kind of discursive accumulation—based on the appearance of following a recent practice-based trend within the third sector—can lead an organisation to be considered `innovative'. Yet the focus on `innovative' practice is part of the creation of economic, social, and affective instability within capitalist realism itself, as the pull to innovate encourages organisations to continually undertake new kinds of projects that they may have no expertise in, ensuring a looping effect: organisations take on too much work, this leads to a lack of capacity, workers feel overworked, the experiences and affects presented in section \ref{subsec:9-2-1} result, and then the need to innovate (to justify the organisation's practice) returns.  The answer to my second research question is that austerity-intensified capitalist realism makes these experiences and affects possible (or probable) through the move towards the "value for money" agenda and youth service provision centered on the production of evaluations. These lead to an atomisation of youth service provision into discrete outcomes and outputs and evaluations that describe how practice creates these outcomes and outputs, which act as justifications of the programme's practice to funders. In order to establish for whom this practice works, potential participants are classified on the basis of their identities. Finally, these justification and classification practices result in performativity and a focus on discursive accumulation at the expense of high-quality practice. 

The contribution that I have made through answering this research question is a grounded theory which describes how these negative experiences are elicited by capitalist realism, and how the third sector has shifted to both create and sustain these experiences. Justification, classification, and discursive accumulation practices each bear relevance to work that is focused on the financialisation of the third sector more generally, and particularly of the application of reforms based on evaluation, "value for money", and new public management ideas within the third sector \citep{mcmullin_challenging_2021}. These reforms focused on creating competition in the hope of creating efficiency and a high level of performance in the third sector, and evaluating this performance through a process that purports to be value-neutral, objective, and self-evidently good. This is based on a construction of evidence and evaluation that imagines already-established social problems waiting in service of optimal solutions, rather than understanding these problems to be actively and socially constructed \citep{greenhalgh_evidence-based_2009}. My work and the new materialist approaches to knowledge (such as Karen Barad's agential realism \citep[p. 45]{barad_meeting_2007}) that I have drawn upon can help to foreground these evaluation practices as being about the active creation of a certain version of reality rather than being an unmediated of it. My research takes this new materialist premise (of evidence being   entangled and co-mingled with the networks of power that create it) and contributes research through direct ethnographic observation that shows just how contingent these evaluations are and how these produce a state of being rather than reflecting one.

\subsection{How can the tools and methods of design be used to respond to the challenges presented by capitalist realism?}
I answered my third research question in chapters \ref{ch:7} and \ref{ch:8}, in which I described two design responses to the challenges presented by capitalist realism. In chapter \ref{ch:7}, I identified what a design response against austerity-intensified capitalist realism would have to be composed of. For workers, I suggested that a successful design response might reduce workloads, support them to do work that they are skilled at, or provide support for workers to build more trusting relationships with managers. For young people perceived to be vulnerable, I proposed that a successful design response might prioritise their agency, listen authentically and follow through on what has been heard, or ensure that they receive the right support. Additionally, I suggested that for these design responses to be successful, they would have to disrupt the functioning of justification, classification, or discursive accumulation practices, or would have to find a way to work around these. As such, a design response to austerity-intensified capitalist realism must find ways to act against the prioritisation of evaluation, the atomisation of projects into outcomes and outputs, the stratification of support based on discrete classifications, or the production of `best practice' through discursive accumulation. Above all else, a design response should address the "slow cancellation of the future \citep[p. 5]{fisher_ghosts_2014} engendered by capitalist realism and create a sense of possibility about the potential of different futures.

In chapter \ref{ch:7}, I went on to describe the \textit{It's Our Future} project, which was designed in conjunction with The Charity. I described the specific constraints upon the project and the limitations this placed upon the exploration of some of these methods—centrally, the re-presentation of justification practices, and the transformation of the project from a digital intervention to an in-person one. I presented the method set that I designed, which focused on the use of idea, summary, and scenario cards, as part of a playful facilitation aid. The methods focused on understanding what would transform young people's lives,  what potential histories might have informed the way that things are right now, to envision and dream a possible future in which those changes have been made, and to identify practical ways of how to build these in the present. The methods were effective at helping young people to develop critical consciousness by reflecting on their lived experiences, but required a greater emphasis on skills, resources, and  creating a sense of possibility about the future, as the dreaming and building the future activities were more limited in scope than they had originally intended to be. Finally, the project was ultimately subsumed by justification, classification and discursive accumulation practices as The Charity continued to center themselves and the image of them as sector leaders and the guardian of the voice of young people perceived to be vulnerable.

After the project, I reflected on these methods and refined them further in a document called \textit{Design Strategies against Justification Practices}, which separated the methods we had used in the project into eight strategies for identifying problems and making alternatives, and four principles for doing this work well. I used this as the starting point for the \textit{fractured signals} project. In contrast to \textit{It's Our Future}'s focus on young people, \textit{fractured signals} focused on people who worked with young people perceived to be vulnerable, and supporting them to reflect on their participation and co-production practices in view of the upcoming \textit{Independent Review of Children's Social Care for England} in the context of the future-focused method set I had developed. Drawing on the ideas of speculative enactment \citep{elsden_speculative_2017} and diegetic prototypes \citep{kirby_future_2010}, I proceeded to create a number of objects that would draw participants into the fiction of the project and more deeply immerse them in the potential futures they were envisioning. \textit{fractured signals} helped participants to develop critical consciousness in the workplace, envision futures that center alternative values, and helped workers to center the experiences of young people perceived to be vulnerable. 

In an attempt to understand how \textit{It's Our Future} and \textit{fractured signals} worked as design responses to austerity-intensified capitalist realism, I proposed that the process used to create them can be considered to be a speculative praxis. This speculative praxis focuses on bringing together speculative design practice and activist praxis. Speculative design practice creates a frame of activity (centered on a possible future, past, or alternate world) that in turn engenders novel possibilities for action and reflection. When deployed in service of an activist cause (i.e. attempting to act outside of the hegemony of austerity-intensified capitalist realism), the experimental actions and reflections participants make can lead to the development of new ideas or capabilities around social change. Speculative praxis is how the tools and methods of design can be used to respond to the challenges presented by capitalist realism.

The contribution that I have made through answering this research question is a method assemblage (in the form of speculative praxis) that can help to address the foreclosure of possibility that is presented by capitalist realism through experimental actions that facilitate "ongoing creation of further relations of possibility" \citep[p. 320]{harrison_future_2020}. My research contributes to work within the critical and speculative design community by more deeply situating critical and speculative design work within paradigms centered on activism and social change. Rather than merely creating individual objects that provoke reflection on possible futures \citep{auger_speculative_2013, dunne_design_2001, dunne_speculative_2013}, I draw on the notion of speculative enactment \citep{elsden_speculative_2017}, speculative interventions \citep{disalvo_irony_2016} and diegetic prototypes \citep{kirby_future_2010} to place speculation within a semi-fictional narrative frame that causes participants to take seriously the capabilities they embody within the frame of the speculation and connect these back to their everyday lives. In essence, the contribution that I have made here consists of creating ways for participants to mentally visit spaces of potential and possibility and take some of this possibility back into their everyday lives with them. Additionally, I have also provided an alternative basis for work centered on speculation with reference to Deleuze and Guattari's ideas of deterritorialization and (re)territorialization. Understanding speculation through deterritorialization and (re)territorializaton helps to place capitalist realism's hegemony in context. Capitalist realism is able to retain hegemony through its "generalised decoding of flows" \citep[p. 153]{deleuze_anti-oedipus:_1983} and the (re)territorialization of capitalistic values which engender commodification and alienation. Speculative activity works in the same way, with different values entering during the (re)territorialization. As such, my research suggests that capital is able to maintain its hegemony as it is a widespread speculation that is no longer believed to be a speculation. Speculative praxis suggests that alternative speculations could come to prominence, weakening or disrupting capital's hegemony. 

\subsection{The thesis' contributions as a whole}
As explained in the preceding three subsections, my thesis makes a number of contributions to both research and practice surrounding the core sites and ideas that it engages with; centrally, social policy, (youth) service provision, and austerity. The core concepts of the thesis—austerity-intensified capitalist realism; justification, classification, and discursive accumulation practices; and speculative praxis—work in collaboration with each other to more clearly elucidate the changes that have taken place in youth service provision as a result of austerity, and to provide a clearer pathway forward for action. Description is itself a political act. In richly describing the affects and experiences of young people perceived to be vulnerable and the workers who support them, the system that gives rise to these affects and experiences, and experimenting with some methods to change these affects, my work has helped to create a clearer articulation of what an affective politics of possibility might require. Actions can be taken by both researchers and practitioners alike on the basis of these descriptions, theories, and methods. 

The notion of austerity-intensified capitalist realism (and the affects and experiences it elicits, as described in chapter \ref{ch:5}) provides a useful meta-narrative for summarising the state of sociopolitics in the late 2000s and 2010s in the United Kingdom. Many ways of interpreting the political dynamics of this period of time—such as neoliberalism, capitalist realism, austerity politics, or the control/disciplinary society—are fruitful for understanding it in closer detail, but each competes with each other for explanatory power. Neoliberalism can be understood to be the disciplinary society, austerity can be understood to be neoliberalism; they are different, and yet inseparable. As such, my framing of austerity-intensified capitalist realism as a resonance machine that accelerates each of these ideologies (and other compatible ideologies) functions as an effective meta-narrative to describe these changes and further sociopolitical changes going forward. For instance, though austerity-intensified capitalist realism described the sociopolitics of the late 2000s and 2010s well, it could be argued that the onset of the COVID-19 pandemic and lockdowns, a further decrease in trust in government, and the ensuing cost-of-living crisis and deepening technological change has led to a change in the most prominent aspects of this resonance machine. Despite this, the resonance machine itself endures; capitalist realism does not cease to exist, neoliberal changes to governance are not reversed, and austerity continues, even as new dynamics are added to the resonance machine. This meta-narrative can help researchers within the social sciences to identify how new ideas, discourses, and policy justifications emerge from old ones, and how old ideas can become resurrected at a moment's notice once they gain a new affective charge.

My grounded theory of justification, classification, and discursive accumulation practices provides a clear description of how capitalist realism operates in practice through evaluation. It therefore contains many suggestions for action for practitioners within the public and third sector evaluation landscape. My work is in alignment with moves within the evaluation world towards deeper understandings of complexity \citep{douthwaite_towards_2017}, away from the notion of outcomes as things that can be `delivered' \citep[p. 983]{lowe_playing_2017}  and towards an evaluation practice that is centered more on relational `learning partnerships' \citep{hesselgreaves_new_2021}. My research certainly suggests that evaluation practitioners within the public and third sector should embrace complexity and relationality. Yet given the current state of public and third sector evaluation, it must be noted that this takes place inside of an environment that will always be looking to discursively accumulate through evaluation practice, no matter how meaningful the practice is. I would therefore encourage evaluation practitioners to explore speculative praxis as part of their complexity-aware, learning-centric, and relational evaluation practices, as the explicit link to the experimental, the speculative, and the affective is a reminder that evaluation itself is a speculative practice that hopes to solidify certain speculations as if they are singular truths, just like capitalist realism.

Speculative praxis is of great use to youth services practitioners, evaluation practitioners, and researchers alike. Speculative praxis takes up Mike Michael's challenge of exploring the "common byways" between speculative design and sociology in "open, multiple, uncertain, and playful ways" \citep[p. 177]{michael_-signing_2012}, and could be considered to be part of the speculative turn taking place in social sciences more generally \citep[p. 1]{williams_abstract_2022}.  Speculation "reconfigures the empirical beyond what seems given in an immediate experience" \citep[p. 2]{williams_abstract_2022}, and as part of an explicitly political praxis, it points towards a political project of opening up possibility through affective design and action. Like \citep[p. 55]{coleman_glitterworlds_2020}, I am suggesting that speculative praxis "provide[s] a means to consider the ways in which methods do and might further be able to world affectively positive futures". Speculative praxis is deliberately close to the experimental, playful, and creative practice traditionally performed by youth workers. It is emergent and becoming, responsive to who and what is there, and seeks to non-directively explore possibility. As such, for youth services practitioners, speculative praxis can be imagined to be a re-politicisation of youth work practice against a backdrop of depoliticisation through professionalisation and bureaucracy; it can become a return to itself. As mentioned above, for evaluation practitioners, speculative praxis can become a mechanism through which evaluation practice becomes less centered on the making-true of certain speculations. For researchers, speculative praxis can be understood to be a coming-together of participatory design, speculative design, action research and activist practice, a method assemblage through which researchers can understand more about the people they are working with whilst designing artefacts and experiences that engender more and new possibilities for those people and themselves.

\section{Limitations}

Although I have strived throughout this research to continually adjust my methodology and data analysis processes to attempt to minimise the limitations of this work, there remain several that are relevant to mention at this stage. A central limitation of this work is that though I have been exploring the impact of austerity on the provision of support services for young people perceived to be vulnerable, it was outside of the scope of this work to conduct direct historical work around the advent of austerity inside of these organisations. As such, there are few insights that are specifically around how post-austerity youth and social work was different to pre-austerity youth and social work. In some places, this did emerge in interviews with participants that have worked in the sector for a long time. This was less significant in my work than it could have been due to my understanding of how these issues build over time. As explored in chapter \ref{ch:2}, the ideas and forces that led to capitalist realism and evaluation-centric youth and social work did not appear out of nowhere in response to the financial crisis and the advent of austerity—these merely amplified existing ideas and social forces. As such, the fact that I do not focus on pre-austerity youth and social work (or even youth and social work during `early austerity') is less significant as I am focused on my participants experiences in the present as they related to these forces. 

Throughout my research, it has been difficult to maintain relationships with organisations who are facing their own set of concerns alongside creating a space for my PhD research. As such, there were likely some `missed opportunities' for the research that could have also yielded generative data around the functioning of capitalist realism and how best to support these kinds of organisations. A notable actor here was Small Steps, who were forced to close during my research due to lack of funding. No doubt, a closer view of the inside of an organisation who is being forced to close due to lack of funding would have been incredibly insightful for understanding how capitalist realism works. Due to the messiness and complexity of the situation (with Small Steps wanting more and more of my time to help avoid the closure of the organisation), I had to step away from my engagement with them in order to not get overwhelmed and continue paying attention to the other organisations I was working with. If this project was being conducted by a wider team, this would have been a brilliant—if difficult, and sad—opportunity to understand the full trajectory of how capitalist realism can affect organisations providing support services. Similarly, it is possible that my relationships with participants in this project and my perceived power as a researcher affected the kind of data I was able to gather. I developed close relationships with many staff members throughout this project, and it is possible that they were more willing to tell me about critical issues due to this relationship. I was perceived positively by the younger participants of this project, who generally felt that they could trust and rely on me. I remained critical about the power I exerted throughout, both with staff and young people. I continually re-established consent during and after times that more critical or sensitive issues were spoken about, and some of the more critical or sensitive things that emerged during my research have been omitted out of respect for participants even though they were willing for that information to feature.

I began this research in 2018 and finished writing my thesis in 2023. Particularly in 2020 and 2021 (critical years for the development of this work), my research plans had to shift significantly due to the advent of the COVID-19 pandemic and the associated public health measures that were taken to protect people. Practically, this meant that follow-up work to \textit{It's Our Future} did not take place in the way that I originally intended, and the follow-up project that did take place (\textit{fractured signals}) had to do so remotely. This did not lead to a drastic transformation of the research itself, as I believe the outcome of the work is still broadly similar to what it would have been otherwise, but it is important to note that this disruption took place. It is fitting perhaps, considering the nature of \textit{fractured signals} (being concerned with possible futures and alternate timelines), that there is an alternate timeline in which the project would not have taken place.

Finally, the central limitation of this project concerns capitalist realism's usefulness as an ongoing analytic. As I have mentioned throughout this chapter, capitalist realism is certainly a useful analytic for understanding the late 2000s and the 2010s, and the way that social forces shaped people's capabilities during this time. Due to the advent of the COVID-19 pandemic, the lockdown measures that followed, a worsening lack of trust in government experienced by many due to government mismanagement during the pandemic, and a deepening of carceral, surveillance-centered, and capability-limiting systems, it is worth questioning whether capitalist realism \textit{remains} as useful as a way to understanding our contemporary sociopolitics. Certainly, capitalist realism at least remains present as part of a resonance machine with many of these new, more prominent forces (as expressed in chapter \ref{ch:2} about neoliberalism), but it may not remain the central structuring force as it perhaps was throughout the 2010s. Future work should explore the ongoing relevance of capitalist realism as an analytic. Despite this, however, speculative praxis should remain a powerful approach for counteracting whatever the dominant capability/possibility-limiting power dynamic of the day is.

\section{Future work: towards an affective politics of possibility}
The contributions made by this thesis (a deeper exploration of capitalist realism; a grounded theory of justification, classification, and discursive accumulation practices; and speculative praxis, a method assemblage for imagining and creating novel possibilities) pose a number of critical questions for the third sector (and beyond), and for contemporary research practice drawing upon both the social sciences and design. I suggest that speculative praxis can help researchers, activists, and frontline workers (and indeed, anyone who uses it) to move their work closer towards creating an affective politics of possibility. By this, I mean that the novel interactions engendered by speculative praxis lead to new possibilities of affect (here meaning both emotion and feeling, and the Deleuzian sense of the "capacity for affecting and being affected" \citep[p. 625]{deleuze_ethology_1992}). Consciously weaving this into the conduct of service provision, research, and life could lead towards a politics constituted not on the "slow cancellation of the future" \citep[p. 5]{fisher_ghosts_2014} but instead on the envisioning and creation of a number  more positively affectively-charged futures. In this section, I indicate potential future work and questions to explore in the third sector and research practice.

\subsection{How can youth service provision be configured differently?}
The research for this thesis has taken place in the context of the provision of youth services. As an ethnography of the infrastructure of youth service provision, I have kept a description of the boundaries of this practice deliberately vague—I have worked with youth workers, social workers, personal advisers, managers, researchers—all manner of professionals occupying distinct roles working towards a similar intention, to improve the experiences or life outcomes for young people perceived to be vulnerable. Yet at its heart, youth service provision is founded on the values and practices of youth work, which I referred to in chapter \ref{ch:1} as being focused on young people's "personal, social, and educational development" \citep[p. 110]{ord_young_2022}. It is clear that the current paradigm of youth service provision— centered on the production of vulnerability through justification, classification, and discursive accumulation practices—runs counter to these goals. Evaluation practice occupies too dominant a role in the provision of youth services.

This is not to suggest that there should be no evaluation of the efficacy of programmes to support young people, but that there needs to be a reconfiguration of the primacy of evaluation and of evidence-based decision-making more generally. Much youth-centred work happens slowly and cannot be meaningfully evaluated at the time of intervention. Many of a person's most formative life experiences happen in their childhood, yes, but they are not necessarily formative \textit{at the time}. Acknowledging the non-linear temporalities of youth work forces us to recognise how little that evaluations conducted at the end of a programme might capture. I recall an assembly I once had at school when I was around 14, when the man who was giving the assembly—a falconer—said something about empathy that resonated deeply with me years after the fact. At the time, I would have thought he was interesting because he had a bird of prey with him, not for anything he said about empathy. We cannot directly predict which actions will lead to which consequences, because youth work is not a science, no matter how much professional evaluation practice may try to codify it into one. What resonates with one group of young people may not land with another. Instead, there is a need for youth service provision that is well-resourced, so that skilled professionals who know how to work well with young people can tailor their approach to specific young people, to try new things and explore new possibilities through their practice.

Speculative praxis may be a productive source of some of these new possibilities. Speculative praxis is already well-aligned to youth service provision, as its roots can be found in the practices of the youth workers I conducted this research with, who already had an intuitive, playful, and creative practice. I see these elements reflected strongly in speculative praxis. As a result, I anticipate that speculative praxis could be a useful methodological resource for critical youth workers trying to retain a political edge to their practice in the context of outcome-led provision. Planning youth work activities through speculative praxis might look like a youth work that uses arts-based methods to think about the future. These kinds of activities can support young people to "explore the affect associated with everyday practices through the multiple activities, rituals and routines that comprise... the micro-intensities of everyday life" \citep[p. 528]{coleman_sensory_2017}. In doing so, young people might gain some critical consciousness of the worlds that they exist in and of their own capacity to remake those worlds. The experiences of young people presented throughout this thesis make exceedingly clear that young people know what they want and need, and are capable of proactively engaging in the forms of support that they think are right for them. The artistic and future focus of speculative praxis can support youth work—whether in the shell of a youth work regime focused on outcomes, or in the prefiguration of a new youth work regime—to pose different kinds of questions about the world that then pose further questions \citep[p. 55]{coleman_glitterworlds_2020}, rather than reducing these questions to a minute change in a singular outcome. 

\subsection{What are the longer-term impacts of the contingency of evaluation data in the third sector?}
The evaluation process that underpins justification, classification, and discursive accumulation practices is broadly consistent with a societal movement towards datafication and increased surveillance \citep{zuboff_age_2019, srnicek_platform_2016}. Evaluation could be understood as one of the central mechanisms through which the experiences of people perceived to be vulnerable are datafied. Although I have referenced it only briefly in this thesis, there are a large number of data-driven technologies being used within this space that rely upon the datafication of everyday experiences. When I first realised how contingently-produced this data was in 2019, I was concerned about the potential of its misuse in automated decision-making (ADM) systems in relation to people perceived to be vulnerable. ADM systems draw upon datafied systems, predictive analytics, machine learning and `artificial intelligence' systems to automatically make decisions about a person, system, or situation. Increasingly, ADM systems are being used within social welfare to deliver automatic decisions (without humans-in-the-loop) about the provision of support services. ADM systems statistically fit new data against a model of older data. As such, they can only function as well as the data that they are initially trained against. 

The evaluation work that has been taking place in the third sector over the past thirteen years (and its relationship to highly atomised and individual outcomes tied to specific types of people for specific types of intervention) constitutes a relatively rich dataset against which an ADM system might be trained. Yet understanding how poor this data \textit{can} be should create doubt around how successful an ADM system trained on this data would be. A relatively recent example of how this can go wrong in the English context is the algorithmic A-Level grading that took place in 2020. This used a statistical model that placed a student and their teacher-estimated grades "in the context of their school and the school’s historical achievement", which on average led to a 39\% decrease in grades than the teacher-estimated grades due to location-based factors, disadvantaging students from poorer areas disproportionately \citep[p. 608]{mead_contested_2023}. Whilst I was concerned about ADM in the third sector in 2019, in the past year or so there has been a larger-scale adoption and public awareness of so-called "artificial intelligence" due to the prevalence of language learning models (LLMs) such as ChatGPT and Google Bard. It feels much more likely that ADM technologies built around existing outcome data will be prominent soon in the third sector. This might happen in a variety of different forms—it could be the process by which a charity decides who to support, the process by which funders decide which charities to fund, or even the basis by which the potential efficacy of a programme is established. Future research into justification, classification and discursive accumulation practices should take datafication and technologisation as a starting point, and consider how these practices will soon be recontextualised within a more deeply technological landscape that may make certain aspects of this process invisible. Paying attention to the ways that technological systems are brought in around the third sector or people perceived to be vulnerable will be integral to understanding the onward trajectory of capitalist realism.

\subsection{Where else do these dynamics exist and how can speculative praxis support action in these areas?}
The insights that I have generated through the grounded theory of justification, classification, and discursive accumulation practices are highly applicable to areas beyond my focus on the third sector. In these areas, an analysis of how capitalist realism operates in that specific site may be fruitful, and speculative praxis could be strategically deployed as a method assemblage to create novel possibilities in these spaces. The hope here would be that by stimulating the use of speculative praxis across multiple sites in society, the practice of building an affective politics of possibility would be distributed across more spaces, increasing its ability to supplant capitalist realism as the dominant mode of engagement with the world. These sites could be found by paying attention to the presence of justification practices, which can be seen in any system where: 
\begin{itemize}
    \item funding is made conditional and competitive,
    \item the conditionality of that funding rests upon the measurement or evaluation of some aspect of a practice, and
    \item the conditionality of funding removes possibilities from actors, thus creating a situation in which ensuring a positive evaluation becomes integral. 
\end{itemize}

The academisation of primary and secondary schools in England evokes these dynamics; \citet[p. 1118]{kauko_evaluation_2015} notes how in fear of poor Ofsted inspections, school managers institute frequent observations of teachers, resulting in a similar environment of distrust and a focus on the production of a positive evaluations. The marketisation of Higher Education similarly evokes these dynamics. More than a decade ago, Burrows \citeyearpar[p. 355]{burrows_living_2012} identified the increasing metricisation of the academy and how academics were beginning to feel more frequently "exhausted, stressed, overloaded, suffering from insomnia, feeling anxious, experiencing feelings of shame, aggression, hurt, [and] guilt". In that paper, Burrows links these experiences to the increasing volume of measurement technologies that are being applied to the Higher Education sector—citation metrics (such as the h-index), research quality assessment (such as the Research Assessment Exercise (RAE) or the Research Excellence Framework (REF)), teaching quality assessment (in the form of the National Student Survey (NSS) and university league tables). Since this paper, teaching quality is also assessed through the Teaching Excellence Framework (TEF) (with a direct link to tuition fee funding), and the applicability of academic knowledge to wider society and business through the Knowledge Exchange Framework (KEF). The increasing metricisation of academic knowledge production, of its "impact" and "public engagement", is emblematic of the capitalist realist paradigm and its impacts.  An exploration of the specific dynamics of capitalist realism and how justification, classification, and discursive accumulation practices manifest in education would be fruitful for understanding another part of a system that ostensibly supports young people's development. Similarly, an understanding of how speculative praxis could be embedded into pedagogy would be a valuable site of methodological innovation.

\subsection{How do speculations become hegemonic?}
As mentioned earlier in this chapter, speculative activity operates in fundamentally the same way as capitalist realism, centered around opening potentials through deterritorialization and closing those potentials through (re)territorialization. It would be worthwhile looking more deeply into how speculations (such as capitalist realism) become hegemonic, how they are able to perpetuate themselves throughout time, and what role knowledge production plays within this process, as it has evidently been central (in the form of evaluation) in this work. There have been initial steps in this direction through, for example, the work of William \citet{connell_neoliberal_2013} in tracking the development of the neoliberal idea over time. Neoliberalism too could be understood as a speculation that became hegemonic—dreamed up in the work of the Mont Pelerin Society, the Institute of Economic Affairs, Friedrich Hayek, Milton Friedman and the Chicago School of Economics. These ideas were then made manifest, first by fringe politicians and then by leading figures such as Thatcher and Reagan, along with media outlets that espoused neoliberal ideas in support of these politicians. Similarly, our modern conception of computing can be traced to a piece of speculative fiction written by Vannevar Bush in \citeyear{bush_as_1945} entitled  "As We May Think". These ideas were picked up by Douglas Engelbart in the Augmentation Research Center, whose team laid the foundations for the computer mouse, the Internet, collaborative working through computers, and hyperlinks. At one point, these ideas—the mouse, the Internet—were speculations that became hegemonic through concerted collaborative action (and capital). Creating an affective politics of possibility would become much easier with a clearer understanding of exactly how these speculations became hegemonic. Researching the ancestry of ideas and systems that are currently hegemonic would involve a kind of Foucauldian archaeology, and would help to expose that current hegemonies remain contingent and changeable. This would also help to clarify how speculations can become more concrete parts of the world. In doing so, this could engender not just new \textit{possibilities}, but entirely new configurations of living.

\section{Concluding remarks}
In this thesis, I have explored capitalist realism as an analytic for understanding the late 2000s and 2010s, particularly in relation to the advent of fiscal austerity. I have provided a deeper theoretical basis for capitalist realism through my exploration of the interrelation of its components, and suggested that austerity acts as an exemplar and intensifier of capitalist realism. I suggested that austerity relied upon the production of vulnerability as the new source and strategy for accumulative activity, and then I explored the impacts of this accumulative activity. I worked with workers and young people to understand their experiences of austerity-intensified capitalist realism and the affects that it elicits within them. I looked more deeply into how these experiences and affects are sustained, proposing that evaluation processes result in the creation of justification, classification and discursive accumulation practices that sustain the hegemony of austerity-intensified capitalist realism. Then, I presented the \textit{It's Our Future} and \textit{fractured signals} projects as speculative design explorations of how to tackle the problems of austerity-intensified capitalist realism. Through these projects, I developed the method assemblage of speculative praxis, which uses speculative design practice within a frame of activist praxis to create new possibilities for action and reflection within a speculative space that are tied to people's actual, everyday lives. 

At the conclusion of Fisher's \textit{Capitalist Realism}, he proposes that the hegemony of capitalist realism means that even small acts that create a sense of novelty can have disproportionately large effects:
\begin{quote}
The very oppressive pervasiveness of capitalist realism means that even glimmers of alternative political and economic possibilities can have a disproportionately great effect. The tiniest event can tear a hole in the grey curtain of reaction which has marked the horizons of possibility under capitalist realism. From a situation in which nothing can happen, suddenly anything is possible again.\citep[pp. 80–81]{fisher_capitalist_2009}
\end{quote}
In this way, the central contribution of this thesis has been a deeper exploration of how to actively create these glimmers of alternative possibilities, to "tear a hole in the grey curtain of reaction", and to create new horizons of possibility. This thesis has acted as a holistic exploration of capitalist realism, understanding more deeply what it is, how it works, and what can be done about it.